\textcolor{Navy}{\textsc{Convexity adjustments with a bit of Malliavin}}

### 2022-10-30 Latex/paper.tex
# new appendix

We suppose, that we have a flow in $T_a < T_p < T_b$ with value $S_{a,b}(T_a)$. Then, the present value of this flow
\begin{align}\label{cms_expedted_value}
P_{ois}(0,T_a)\mathbb{E}^{\mathbb{Q}^{T_{a}}}\left(S_{a,b}(T_a) P_{ois}(T_a,T_p) \right) &= 01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \frac{P_{ois}(T_a,T_p)}{01(T_a,T_a,T_b) }\right) \nonumber \\
&= 01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) M(T_a,T_p)\right)
\end{align}
where $M(t, T_p)= \frac{P_{ois}(t,T_p) }{01(t,T_a,T_b)} $. In order to reduce the complexity to explain the movement od the forward curve, it is a common pratice to asumme that
\begin{equation*}
M(t) = f(S^{ois}_{a,b}(t))
\end{equation*}
where $f(\cdot)$ is known as mapping function. There is a extensive literature how to define this function (see Piterbarg Volume III), in later we will see some particular examples. Under the last assumption and applying Clark-Ocone to $f(S_{a,b}(t))$ we get
\begin{align*}
f(S^{ois}_{a,b}(T_a)) &= \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(f(S^{ois}_{a,b}(T_a)\right) + \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left( D_s (f(S^{ois}_{a,b}(T_a)) \right) dW^{01(a,b)}_{s} \\
&= \frac{P_{ois}(0,T_p) }{01(0,T_a,T_b)} + \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left(f^{\prime}(S^{ois}_{a,b}(T_a) \partial_{x}S^{ois}_{a,b}(T_a) D_s x_{T_a} \right) dW^{01(a,b)}_{s}. 
\end{align*}
Therefore, we can define the convexity adjustment for a CMS the next way
\begin{align*}
CA_{CMS}(T_a,T_b) = \\
01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left( f^{\prime}(S^{ois}_{a,b}(T_a)) \partial_{x}S^{ois}_{a,b}(T_a) D_s x_{T_a} \right) dW^{01(a,b)}_{s} \right)
\end{align*}
Now if we apply the adjoint operator of the Malliavin derivative (see Elisa-David) we get

\begin{align*}
&CA_{CMS}(T_a,T_b)  \\
&=01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( \int_{0}^{T_a} \partial_{x}S_{a,b}(T_a) D_s x_{T_a} \mathbb{E}_s^{01(a,b)}\left(f^{\prime}(S^{ois}_{a,b}(T_a)) \partial_{x}S^{ois}_{a,b}(T_a) D_s x_{T_a} \right) ds \right) \nonumber \\
&\approx 01(0,T_a,T_b)  \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( \int_{0}^{T_a} \partial_{x}S_{a,b}(T_a, x_0, y_0) \partial_{x}S^{ois}_{a,b}(T_a, x_0, y_0) f^{\prime}(S^{ois}_{a,b}(T_a, x_0, y_0)  D_s x_{T_a} \mathbb{E}_s^{01(a,b)}\left(D_s x_{T_a} \right) ds \right) \nonumber \\
& \approx 01(0,T_a,T_b)  \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( \int_{0}^{T_a} \partial_{x}S_{a,b}(T_a, x_0, y_0) \partial_{x}S^{ois}_{a,b}(T_a, x_0, y_0) f^{\prime}(S^{ois}_{a,b}(T_a, x_0, y_0) \beta(s,T_a,x_0,\hat{y}_{s})  D_s x_{T_a}  ds \right)
\end{align*}

\begin{remark}\label{drift_01_spot_measure}
Before to continue, we must to calculate the Girsanov's measure change from $\mathbb{Q}$ to $\mathbb{Q}^{01(a,b)}$. In order to achieve this target, we will use a continuous version of $01(t,T_a,T_b)$ i.e
\begin{equation*}
01^{c}(t,T_a,T_b) = \int_{T_a}^{T_b} P_{ois}(t,u) du.
\end{equation*}
It is easy to see that if we define $z_t=\frac{01^{c}(t,T_a,T_b)}{\beta_t}$ and apply Itô's formula we get
\begin{equation*}
dW^{01(a,b)}_t = dW^{\mathbb{Q}}_t + \lambda_{t}dt 
\end{equation*}
where $\lambda_t = \frac{\int_{T_a}^{T_b} P_{ois}(t,u) \nu(t,u) du}{01^{c}(t,T_a,T_b)}$. Then we can do the next approximation for $\lambda_t$
\begin{equation*}
\hat{\lambda}_t \approx \frac{\int_{T_a}^{T_b} P_{ois}(t,u,x_0,\hat{y}_t) \nu(t,u) du}{01^{c}(t,T_a,T_b,x_0,\hat{y}_t)} 
\end{equation*}
\end{remark}
Now, if we apply (\ref{drift_01_spot_measure}) we get that 
\begin{equation*}
\mathbb{E}_s^{\mathbb{Q}^{01(a,b)}}\left( D_s x_{T_a} \right) \approx \beta(s,T_a,x_0,\hat{y}_{s}) \exp\left(-\int_{s}^{T_a} \frac{\int_{T_a}^{T_b} P_{ois}(u,u^{\prime},x_0,\hat{y}_u) \nu(t,u^{\prime}) du^{\prime}}{01^{c}(u,T_a,T_b,x_0,\hat{y}_u)} \partial_x \beta(u,t_0,x_0,\hat{y}_u) du \right)
\end{equation*}
Therefore we have the next for the convexity adjustment

\fboxsep1em
\fbox{\parbox{435pt}
{

\begin{align}\label{cms_adjustment}
&CA_{CMS}(T_a,T_b) \nonumber \\
&\approx 01(0,T_a,T_b) \int_{0}^{T_a} \partial_{x}S_{a,b}(T_a, x_0, y_0) \partial_{x}S^{ois}_{a,b}(T_a, x_0, y_0)  f^{\prime}(S^{ois}_{a,b}(T_a, x_0, y_0)) \beta^{2}(s,T_a,x_0,\hat{y}_{s}) \Omega(s, T_a)    ds
\end{align}
with 
$$\Omega(s, T_a) = \exp\left(-2\int_{s}^{T_a} \frac{\int_{T_a}^{T_b} P_{ois}(u,u^{\prime},x_0,\hat{y}_u) \nu(t,u^{\prime}) du^{\prime}}{01^{c}(u,T_a,T_b,x_0,\hat{y}_u)} \partial_x \beta(u,t_0,x_0,\hat{y}_u) du \right) 
$$
}}
\begin{example}
In ghe case of a Hull-White model, we showed in the example  (\ref{example_convexity_hw_ois}) that 
$$
\partial_x \beta(u,t_0,x_0,\hat{y}_u)=0
$$
\end{example}
Therefore (\ref{cms_adjustment}) is reduced to
\begin{equation}\label{cms_general_convexity}
01(0,T_a,T_b) \int_{0}^{T_a} \partial_{x}S_{a,b}(T_a,x_0,y_0) \partial_{x}S^{ois}_{a,b}(T_a,x_0,y_0) f^{\prime}(S^{ois}_{a,b}(T_a,x_0,y_0)) \beta^{2}(s,T_a,x_0,\hat{y}_{s}) ds
\end{equation}
A common practice in market, it is suppose that $f(x)=\alpha x + \beta$ (TSR model). We must to impose two equations in order to get $\alpha$ and $\beta$. The first equation follows straightforward from the definition of $M(t,T_p)$. Since, $M(t,T_p)$ is a $01(a,b)-$martingale we must have that
\begin{equation*}
\mathbb{E}^{01(a,b)}\left(\alpha S^{ois}_{a,b}(T_a) + \beta \right) = \frac{P_{ois}(0,T_p)}{01(0,T_a,T_b)}.
\end{equation*}
Therefore
\begin{equation*}
\beta = \frac{P_ois(0,T_p)}{01(0,T_a,T_b,x_0,y_0)} - \alpha S^{ois}_{a,b}(0,x_0,y_0).
\end{equation*}
Under a separable HJM dynamic we must have that
\begin{equation*}
\alpha \partial_{x} S^{ois}_{a,b}(T_a,x_0,y_0) = - M(0,T_p)\left(G(T_a,T_p)+\frac{\partial_x 01(T_a,T_a,T_b,x_0,y_0)}{01(T_a,T_a,T_b,x_0,y_0)}\right).
\end{equation*}
Then
\begin{equation*}
\alpha = -\frac{M(T_a,T_p)\left(G(T_a,T_p)+\frac{\partial_x 01(T_a,T_a,T_b,x_0,y_0)}{01(T_a,T_a,T_b,x_0,y_0)}\right)}{\partial_{x} S^{ois}_{a,b}(T_a,x_0,y_0)}.
\end{equation*}
Then from the last equalities, we can approximate the convexity adjustment of a CMS rate as
\begin{align*}
CA_{CMS}(T_a,T_b)\\
\approx - P_{ois}(0,T_p,x_0,y_0) \left(G(T_a,T_p) +\frac{\partial_x 01(T_a,T_a,T_b,x_0,y_0)}{01(T_a,T_a,T_b,x_0,y_0)}\right) \partial_{x}S_{a,b}(0,x_0,y_0) \int_{0}^{T_a}  \beta^{2}(s,T_a,x_0,\hat{y}_{u}) ds
\end{align*}
In the next figure, we can see the convexity adjustment for a CMS where the tenor for the underlying swap is 5Y using the last approximation and Monte Carlo method

\section{Conclusion}\label{sec:Conclusion}

>>>>

We suppose, that we have a flow in $T_a < T_p < T_b$ with value $S_{a,b}(T_a)$. Then, the present value of this flow
\begin{align}\label{cms_expedted_value}
P_{ois}(0,T_a)\mathbb{E}^{\mathbb{Q}^{T_{a}}}\left(S_{a,b}(T_a) P_{ois}(T_a,T_p) \right) &= 01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \frac{P_{ois}(T_a,T_p)}{01(T_a,T_a,T_b) }\right) \nonumber \\
&= 01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) M(T_a,T_p)\right)
\end{align}
where $M(t, T_p)= \frac{P_{ois}(t,T_p) }{01(t,T_a,T_b)} $. In order to reduce the complexity to explain the movement od the forward curve, it is a common pratice to asumme that
\begin{equation*}
M(t) = f(S^{ois}_{a,b}(t))
\end{equation*}
where $f(\cdot)$ is known as mapping function. There is a extensive literature how to define this function (see Piterbarg Volume III), in later we will see some particular examples. Under the last assumption and applying Clark-Ocone to $f(S_{a,b}(t))$ we get
\begin{align*}
f(S^{ois}_{a,b}(T_a)) &= \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(f(S^{ois}_{a,b}(T_a)\right) + \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left( D_s (f(S^{ois}_{a,b}(T_a)) \right) dW^{01(a,b)}_{s} \\
&= \frac{P_{ois}(0,T_p) }{01(0,T_a,T_b)} + \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left(f^{\prime}(S^{ois}_{a,b}(T_a) \partial_{x}S^{ois}_{a,b}(T_a) D_s x_{T_a} \right) dW^{01(a,b)}_{s}. 
\end{align*}
Therefore, we can define the convexity adjustment for a CMS the next way
\begin{align*}
CA_{CMS}(T_a,T_b) = \\
01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left( f^{\prime}(S^{ois}_{a,b}(T_a)) \partial_{x}S^{ois}_{a,b}(T_a) D_s x_{T_a} \right) dW^{01(a,b)}_{s} \right)
\end{align*}
Now if we use again the Clark-Ocone representation, but in this case for $S_{a,b}(T_a)$, we can do the next approximation
\begin{align*}
CA_{CMS}(T_a,T_b) &\approx 01(0,T_a,T_b)  f^{\prime}(S^{ois}_{a,b}(0)) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \left( S^{ois}_{a,b}(T_a) - S^{ois}_{a,b}(0)\right)\right) \\
&= 01(0,T_a,T_b)  f^{\prime}(S^{ois}_{a,b}(0)) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S^{ois}_{a,b}(T_a)S_{a,b}(T_a) -  S_{a,b}(0) S^{ois}_{a,b}(0)\right)
\end{align*}
Where we have used that $S_{a,b}(t)$ and $S^{ois}_{a,b}(T_a)$ are $01(a,b)$-martingale. Also, if we use Itô formula we get that
\begin{align*}
dS^{ois}_{a,b}(t,x_t,y_t) &= \partial_{x}S^{ois}_{a,b}(t,x_t,y_t)\eta(t,x_t,y_t)dW^{01(a,b)}  \\
dS_{a,b}(t,x_t,y_t) &= \partial_{x}S_{a,b}(t,x_t,y_t)\eta(t,x_t,y_t)dW^{01(a,b)} 
\end{align*}
with initial condition respectivaly $S^{ois}_{a,b}(0)$ and $S_{a,b}(0)$. Then we have that
\begin{align*}
\mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S^{ois}_{a,b}(T_a)S_{a,b}(T_a) \right) &= \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(\int_0^{T_a} \partial_{x}S_{a,b}(u,x_u,y_u) \partial_{x}S^{ois}_{a,b}(u,x_u,y_u)  \eta^{2}(u,x_u,y_u)
du \right)  + S_{a,b}(0) S^{ois}_{a,b}(0) \\
&\approx  \partial_{x}S_{a,b}(0) \partial_{x}S^{ois}_{a,b}(0)\int_0^{T_a} \eta^{2}(u,x_0,\hat{y}_u) + S_{a,b}(0) S^{ois}_{a,b}(0).
du
\end{align*}
Therefore, if se use the last equality we can approximate $CA_{CMS}(T_a,T_b)$ the next way

\fboxsep1em
\fbox{\parbox{435pt}
{
\begin{equation}\label{cms_adjustment}
CA_{CMS}(T_a,T_b) \approx 01(0,T_a,T_b)  f^{\prime}(S^{ois}_{a,b}(0)) \partial_{x}S_{a,b}(0) \partial_{x}S^{ois}_{a,b}(0)\int_0^{T_a} \eta^{2}(u,x_0,\hat{y}_u) du
\end{equation}
}}

\begin{example}
In ghe case of a Hull-White model, we showed in the example  (\ref{example_convexity_hw_ois}) that 
$$
\eta(t,x_t, y_t) = \sigma\exp(-kt)
$$
\end{example}
Therefore (\ref{cms_adjustment}) is reduced to
\begin{equation}\label{hullwhite_cms_convexity}
01(0,T_a,T_b)  f^{\prime}(S^{ois}_{a,b}(0)) \partial_{x}S_{a,b}(T_a) \partial_{x}S^{ois}_{a,b}(T_a) \frac{ \sigma^2(1-\exp(-2kT_a))}{2k} 
\end{equation}
A common practice in market, it is suppose that $f(x)=\alpha x + \beta$ (TSR model). We must to impose two equations in order to get $\alpha$ and $\beta$. The first equation follows straightforward from the definition of $M(t,T_p)$. Since, $M(t,T_p)$ is a $01(a,b)-$martingale we must have that
\begin{equation*}
\mathbb{E}^{01(a,b)}\left(\alpha S^{ois}_{a,b}(T_a) + \beta \right) = \frac{P_{ois}(0,T_p)}{01(0,T_a,T_b)}.
\end{equation*}
Therefore
\begin{equation*}
\beta = \frac{P_{ois}(0,T_p)}{01(0,T_a,T_b,x_0,y_0)} - \alpha S^{ois}_{a,b}(0,x_0,y_0).
\end{equation*}
Under a separable HJM dynamic we must have that
\begin{equation*}
\alpha \partial_{x} S^{ois}_{a,b}(0) = - M(0,T_p)\left(G(T_a,T_p)+\frac{\partial_x 01(0,T_a,T_b)}{01(0,T_a,T_b)}\right).
\end{equation*}
Then
\begin{equation*}
\alpha = -\frac{M(0,T_p)\left(G(T_a,T_p)+\frac{\partial_x 01(0,T_a,T_b)}{01(0,T_a,T_b)}\right)}{\partial_{x} S^{ois}_{a,b}(0)}.
\end{equation*}
Then from the last equalities, we can approximate the convexity adjustment of a CMS rate as
\begin{align*}
CA_{CMS}(T_a,T_b) \\ 
\approx 01(0,T_a,T_b) \alpha \partial_{x}S_{a,b}(0) \partial_{x}S^{ois}_{a,b}(0) \frac{ \sigma^2(1-\exp(-2kT_a))}{2k}  \\   
= - P_{ois}(0,T_p) \left(G(T_a,T_p)+\frac{\partial_x 01(0,T_a,T_b)}{01(0,T_a,T_b)}\right) \partial_{x}S_{a,b}(0)  \frac{ \sigma^2(1-\exp(-2kT_a))}{2k}
\end{align*}
In the next figure, we can see the convexity adjustment for a CMS where the tenor for the underlying swap is 5Y using the last approximation and Monte Carlo method

\section*{Appendix}
\appendix
\renewcommand{\thesection}{\Alph{section}.\arabic{section}}
\section{Malliavin derivative calculations}

\subsection{Approximation of $\mathbb{E}_s^{T_p}\left(D_s x_{T_a}\right)$}
\label{expected_forward_measure_malliavin_derivative_x_t}
From (\ref{short_rate_cheyette}) is easy to show that
\begin{equation*}
x_{T_a} = \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) y_u du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,x_u,y_u) dW_u^{\mathbb{Q}}  
\end{equation*}
Therefore, we have that
